---
title: "PSY 8712 Week 8 Project"
author: "Mackenzie R Nickle"
date: "2024-03-15"
output: 
  html_document:
      df_print: paged
---

# **Reproducible Image and Online Resources**
An image of this project as of *date* can be accessed by clicking <INSERT IMAGE LINK>
An interactive web app is available by clicking <INSERT SHINY APP> instead

# **Script Settings and Resources**
```{r, message=FALSE}
library(tidyverse)
library(shiny)
library(rsconnect)
```

# **Data Import and Cleaning**
For data import and cleaning, I followed the code from last week with the exception of reverse coding item five, which I did the way I was taught in a previous stats class by just subtracting each item by one more than the maximum for that number. I also created the average scores needed in the data visualization section by using rowMeans as I have done it that way in the past. 
```{r, message=FALSE}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(timestart= ymd_hms(timeStart),
         q5= 6-q5,
         across(starts_with("q"), as.numeric),
         condition= factor(condition,
                           levels=c("A","B","C"),
                           labels= c("Block A","Block B","Control")),
         gender= factor(gender,
                        levels=c("M","F"),
                        labels= c("Male","Female"))) %>% 
  mutate(avg_q1q6= rowMeans(select(., q1:q6)),
         avg_q8q10= rowMeans(select(., q8:q10)))
```

# **Visualization**

```{r, echo=FALSE, message=FALSE}
select(week8_tbl, paste0("q", 1:6))

week8_tbl %>%
  ggplot(aes(avg_q1q6, avg_q8q10)) + 
  geom_point() +
  geom_smooth(method=lm, color="purple", se=TRUE) +
  labs(x="Mean Scores on Q1-Q6",
       y= "Mean Scores on Q8-Q10",
       title= "Figure 1")
```

# **Analysis**


```{r, echo=FALSE}
cor.test(week8_tbl$avg_q1q6,week8_tbl$avg_q8q10)
cor1 <-cor.test(week8_tbl$avg_q1q6,week8_tbl$avg_q8q10)$estimate
cor2 <- format(cor1, digits=1)
cor2 <- sub("^0", "", sprintf("%.2f", cor1))
```
Based on the correlation test, the correlation between the mean scores for questions 1-6 and for the mean scores for questions 8-10 is `r cor2`. The p-value was not significant at .56. To format the correlation, I used format() from the class slides. 

# **Data Export**

```{r}
week8_tbl %>%
  select(timeEnd, gender, avg_q1q6, avg_q8q10) %>%
  write.csv("../shiny/w8shiny.csv")
```

